---
Author: "Rita Alvarez Martinez"
Date: "October 5th"
Title: "Airline safety dataset"
output: html_document
---


## Getting the dataset from the web
mydat <-read.csv('https://raw.githubusercontent.com/fivethirtyeight/data/master/airline-safety/airline-safety.csv')

## Compare means for incidents between 1985 and 1999 and between 2000 and 2014
mean(mydat$incidents_85_99)
mean(mydat$incidents_00_14)

## Compare means for fatal accidents between 1985 and 1999 and between 2000 and 2014
mean(mydat$fatal_accidents_85_99)
mean(mydat$fatal_accidents_00_14)

## Compare means for fatalities between 1985 and 1999 and between 2000 and 2014
mean(mydat$fatalities_85_99)
mean(mydat$fatalities_00_14)


##Create totals for incidents, fatal accidents and fatalities
mydat <- transform (mydat,
total_incidents = incidents_85_99 + incidents_00_14,
total_fatal_accidents = fatal_accidents_85_99 + fatal_accidents_00_14,
total_fatalities = fatalities_85_99 + fatalities_00_14)

##Creating index to identify potential dangerous airlines to flight with
mydat <- transform (mydat,
index_inc_psk= (total_incidents/avail_seat_km_per_week)*1000000000,
index_fat_acc_psk= (total_fatal_accidents/avail_seat_km_per_week)*1000000000,
index_fat_psk= (total_fatalities/avail_seat_km_per_week)*1000000000)

sort1.mydat <- mydat[order(mydat$index_inc_psk), ]
sort2.mydat <- mydat[order(mydat$index_fat_acc_psk), ]
sort3.mydat <- mydat[order(mydat$index_fat_psk), ]

## Including Plots

You can also embed plots, for example:

```{r plot1, echo=FALSE}
plot(mydat$avail_seat_km_per_week, mydat$total_incidents)
```

```{r echo=FALSE}
plot(mydat$avail_seat_km_per_week, mydat$total_fatal_accidents)
```

```{r echo=FALSE}
plot(mydat$avail_seat_km_per_week, mydat$total_fatalities)
```
